Figures and tables for paper

### 2021-12-14 analysis/04_figs-tables.Rmd
Finished remaining contrasts through 5f

```{r contrasts-hypothesis04c}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))
draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
    "crackdown emergency small donors - crackdown human rights wealthy donors" = 
      (crackdown) - 
      (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors +
         humanrights_crackdown_wealthydonors),
    "crackdown emergency small donors - crackdown human rights government grants" = 
      (crackdown) - 
      (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants +
         humanrights_crackdown_grants),
    emergency_environment_wealthydonors = 
      (crackdown) - 
      (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors +
         environment_crackdown_wealthydonors),
    emergency_environment_grants = 
      (crackdown) - 
      (crackdown + government_grants + environment + crackdown_environment + crackdown_grants +
         environment_crackdown_grants),
    refugee_humanrights_wealthydonors = 
      (crackdown + refugee_relief + crackdown_refugee) - 
      (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors +
         humanrights_crackdown_wealthydonors),
    refugee_humanrights_grants = 
      (crackdown + refugee_relief + crackdown_refugee) - 
      (crackdown + government_grants + human_rights + crackdown_humanrights + crackdown_grants +
         humanrights_crackdown_grants),
    refugee_environment_wealthydonors = 
      (crackdown + refugee_relief + crackdown_refugee) - 
      (crackdown + few_wealthy_private_donors + environment + crackdown_environment + crackdown_wealthydonors +
         environment_crackdown_wealthydonors),
    refugee_environment_grants = 
      (crackdown + refugee_relief + crackdown_refugee) - 
      (crackdown + government_grants + environment + crackdown_environment + crackdown_grants +
         environment_crackdown_grants)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    emergency_humanrights_wealthydonors:refugee_environment_grants, 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

holding every other attribute constant

@@

#### Hypothesis 5a, Organizational Practices

@@

```{r contrasts-hypothesis05a}
# Pull the posterior draws for organizational practices
# Pull the relevant posterior draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "intercept.rds"))

# Compute the contrasts
contrasts <- tibble(
  fin_transparency = draws %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(level == "Accountability") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer(fin_transparency, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

holding every other attribute constant

Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.

#### Hypothesis 5b, Relationship with Host Government, Organizational Practices

@@

```{r contrasts-hypothesis05b}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))

# Pull the posterior draws for organizational practices*government crackdown interaction
# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  fin_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  ) %>% mutate(
    fin_transparency_criticized = (fin_transparency + criticized + fin_transparency_criticized) - (criticized),
    fin_transparency_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown) - (crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(financial_transparency_criticized:financial_transparency_crackdown, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

```

holding every other attribute constant

The contrasts for hypothesis 5b provide evidence that donors are more willing to donate to organizations which are criticized or under crackdown and are also financially transparent.

#### Hypothesis 5c, Relationship with Host Government, Organizational Practices, and Funding Sources

@@

```{r contrasts-hypothesis05c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
# Lower order interaction draws
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))

# Pull the posterior draws for organizational practices*funding sources*government crackdown interaction
# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws_4b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws_4b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_smalldonors_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  ) %>%
  mutate(
  fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) - (fin_transparency + criticized + few_wealthy_private_donors + criticized_wealthydonors + fin_transparency_criticized + fin_wealthydonors_criticized),

  fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) -  (fin_transparency + criticized + government_grants + criticized_grants + fin_transparency_criticized + fin_grants_criticized),

  fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + few_wealthy_private_donors + crackdown_wealthydonors + fin_transparency_crackdown + fin_wealthydonors_crackdown),

  fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (fin_transparency + crackdown + government_grants + crackdown_grants + fin_transparency_crackdown + fin_grants_crackdown),

# additional contrasts to compare financial transparency to no transparency    
  not_fin_smalldonors_wealthydonors_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) - (criticized + few_wealthy_private_donors + criticized_wealthydonors),

  not_fin_smalldonors_grants_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_smalldonors_criticized) -  (criticized + government_grants + criticized_grants),

  not_fin_smalldonors_wealthydonors_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (crackdown + few_wealthy_private_donors + crackdown_wealthydonors),

  not_fin_smalldonors_grants_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_smalldonors_crackdown) - (crackdown + government_grants + fin_transparency_crackdown + fin_grants_crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_smalldonors_wealthydonors_criticized:not_fin_smalldonors_grants_crackdown, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05c.png",#
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

holding every other attribute constant

Only fin_smalldonors_grants_crackdown contains 0 within its credibility interval. Since all other contrasts are positive and do not contain 0 within their credibility intervals, there is evidence supporting that donors are more willing to donate to NGOs that are criticized by the government/under government crackdown, are financially transparent, and are funded primarily by numerous small private donors.

#### Hypothesis 5d, Relationship with Host Government, Organizational Practices, and Issue Area

@@

```{r contrasts-hypothesis05d}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
# Lower-order interactions
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

# Pull the posterior draws for organizational practices*issue area*government crackdown interaction
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include financial transparency

contrasts_int <- tibble(
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized_environment = draws_3b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_humanrights = draws_3b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws_3b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  fin_transparency_criticized = draws_5b %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_transparency_crackdown = draws_5b %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_emergency_criticized) - (fin_transparency + criticized + environment + fin_transparency_criticized + criticized_environment + fin_environment_criticized),

  fin_emergency_humanrights_criticized = (fin_transparency + criticized + fin_transparency_criticized + fin_emergency_criticized) - (fin_transparency + criticized + human_rights + fin_transparency_criticized + criticized_humanrights + fin_humanrights_criticized),

  fin_emergency_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + environment + fin_transparency_crackdown + crackdown_environment + fin_environment_crackdown),

  fin_emergency_humanright_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + fin_emergency_crackdown) - (fin_transparency + crackdown + human_rights + fin_transparency_crackdown + crackdown_humanrights + fin_humanrights_crackdown),

  fin_refugee_environment_criticized = (fin_transparency + criticized + fin_transparency_criticized + criticized_refugee + fin_refugee_criticized) - (fin_transparency + criticized + environment + fin_transparency_criticized + criticized_environment + fin_environment_criticized),

  fin_refugee_humanright_criticized = (fin_transparency + criticized + fin_transparency_criticized + criticized_refugee + fin_refugee_criticized) - (fin_transparency + criticized + human_rights + fin_transparency_criticized + criticized_humanrights + fin_humanrights_criticized),

  fin_refugee_environment_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + crackdown_refugee + fin_refugee_crackdown) - (fin_transparency + crackdown + environment + crackdown_environment + fin_transparency_crackdown + fin_environment_crackdown),

  fin_refugee_humanright_crackdown = (fin_transparency + crackdown + fin_transparency_crackdown + crackdown_refugee + fin_refugee_crackdown) - (fin_transparency + crackdown + human_rights + fin_transparency_crackdown + crackdown_humanrights + fin_humanrights_crackdown)
)

# Plot the contrasts
contrasts_int %>%
  pivot_longer(fin_emergency_environment_criticized:fin_refugee_humanright_crackdown, names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

The contrasts don't seem to be properly calculated, so no conclusion at this time.

holding every other attribute constant

#### Hypothesis 5e, Relationship with Host Government, Organizational Practices, Issue Area, and Funding Sources

@@

```{r contrasts-hypothesis05e}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds"))
# Lower-order interactions
draws_5b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
draws_5c <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))
draws_5d <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))
# Pull the posterior draws for organizational practices*funding*issue area*government crackdown interaction
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# All interactions include small donors
# All interactions include financial transparency

>>>>

```{r contrasts-hypothesis04c}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))

# Reference Level = Emergency Response
# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts_int <- tibble(
  # Attribute levels
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  # Hypothesis 4c
  emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "wealthy donors environment - small donors emergency" = 
      few_wealthy_private_donors + environment,
    "wealthy donors human rights - small donors emergency" = 
      few_wealthy_private_donors + human_rights,
    "wealthy donors refugee relief - small donors emergency" = 
      few_wealthy_private_donors + refugee_relief,
    "crackdown wealthy donors environment - crackdown small donors emergency" = 
      (few_wealthy_private_donors + environment + crackdown + environment_crackdown_wealthydonors) - (crackdown + emergency_crackdown_wealthydonors),
    "crackdown wealthy donors human rights - crackdown small donors emergency" = 
      (few_wealthy_private_donors + human_rights + crackdown + humanrights_crackdown_wealthydonors) - (crackdown + emergency_crackdown_wealthydonors),
    "crackdown wealthy donors refugee relief - crackdown small donors emergency" = 
      (few_wealthy_private_donors + refugee_relief + crackdown + refugee_crackdown_wealthydonors) - (crackdown + emergency_crackdown_wealthydonors),
    "government grants environment - small donors emergency" = 
      government_grants + environment,
    "government grants human rights - small donors emergency" = 
      government_grants + human_rights,
    "government grants refugee relief - small donors emergency" = 
      government_grants + refugee_relief,
    "crackdown government grants environment - crackdown small donors emergency" = 
      (government_grants + environment + crackdown + environment_crackdown_grants) - (crackdown + emergency_crackdown_grants),
    "crackdown government grants human rights - crackdown small donors emergency" = 
      (government_grants + human_rights + crackdown + humanrights_crackdown_grants) - (crackdown + emergency_crackdown_grants),
    "crackdown government grants refugee relief - crackdown small donors emergency" = 
      (government_grants + refugee_relief + crackdown + refugee_crackdown_grants) - (crackdown + emergency_crackdown_grants)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "wealthy donors environment - small donors emergency":"crackdown government grants refugee relief - crackdown small donors emergency", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

There an increase in likelihood to donate in general when NGOs are funded by government grants, which we've seen separately, though the difference isn't significant when accounting for the NGOs being under crackdown, holding every other attribute constant. We also see that refugee relief continues to be seen as contentious as the environment. Interestingly, the median likelihood to donate is somewhat normalized across issue areas when the NGOs are under crackdown and all funded by wealthy donors.

@@

#### Hypothesis 5a, Financial Transparency

@@

```{r contrasts-hypothesis05a}
# Reference Level = No financial transparency
# Compute the contrasts
contrasts <- tibble(
  "financial transparency - no financial transparency" = draws_intercept %>% filter(level == "Financial transparency") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer("financial transparency - no financial transparency", names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors show an increased likelihood to donate to NGOs that are financially transparent, holding every other attribute constant.

#### Hypothesis 5b, Relationship with Host Government and Financial Transparency

@@

```{r contrasts-hypothesis05b}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds"))

# Reference Level = No financial transparency
# Reference Level = Friendly relationship with government
contrasts_int <- tibble(
  # Attribute levels
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  # Hypothesis 5b
  fin_transparency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_transparency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "financial transparency - no financial transparency" = fin_transparency,
    "criticized financial transparency - criticized no financial transparency" = 
      (fin_transparency + criticized + fin_transparency_criticized) - (criticized),
    "crackdown financial transparency - crackdown no financial transparency" = 
      (fin_transparency + crackdown + fin_transparency_crackdown) - (crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "financial transparency - no financial transparency":"crackdown financial transparency - crackdown no financial transparency", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

There is no increased willingness to donate to NGOs that are criticized or under government crackdown that are also financially transparent, holding every other attribute constant.

#### Hypothesis 5c, Relationship with Host Government, Financial Transparency, and Funding Sources

@@

```{r contrasts-hypothesis05c}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds"))

# Reference Level = No financial transparency
# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations
contrasts_int <- tibble(
  # Attribute levels
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  # Hypothesis 5c
  fin_smalldonors_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "financially transparent small donors - not financially transparent small donors" = 
      (fin_transparency),
    "financially transparent wealthy donors - not financially transparent wealthy donors" = 
      (fin_transparency + few_wealthy_private_donors) - (few_wealthy_private_donors),
    "financially transparent government grants - not financially transparent government grants" = 
      (fin_transparency + government_grants) - (government_grants),
    "criticized financially transparent small donors - criticized not financially transparent small donors" = 
      (fin_transparency + criticized + fin_smalldonors_criticized) - (criticized),
    "criticized financially transparent wealthy donors - criticized not financially transparent wealthy donors" =
      (fin_transparency + few_wealthy_private_donors + criticized + fin_wealthydonors_criticized) - (few_wealthy_private_donors + criticized),
    "criticized financially transparent government grants - criticized not financially transparent government grants" = 
      (fin_transparency + government_grants + criticized + fin_grants_criticized) - (government_grants + criticized),
    "crackdown financially transparent small donors - crackdown not financially transparent small donors" = 
      (fin_transparency + crackdown + fin_smalldonors_crackdown) - (crackdown),
    "crackdown financially transparent wealthy donors - crackdown not financially transparent wealthy donors" =
      (fin_transparency + few_wealthy_private_donors + crackdown + fin_wealthydonors_crackdown) - (few_wealthy_private_donors + crackdown),
    "crackdown financially transparent government grants - crackdown not financially transparent government grants" = 
      (fin_transparency + government_grants + crackdown + fin_grants_crackdown) - (government_grants + crackdown),
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "financially transparent small donors - not financially transparent small donors":"crackdown financially transparent government grants - crackdown not financially transparent government grants", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis05c.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

There is no increased willingness to donate to NGOs that are criticized or under government crackdown when they are also financially transparent and funded by numerous small private donors, holding every other attribute constant.

#### Hypothesis 5d, Relationship with Host Government, Financial Transparency, and Issue Area

@@

```{r contrasts-hypothesis05d}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds"))

# Reference Level = No financial transparency
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
contrasts_int <- tibble(
  # Attribute levels
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  # Hypothesis 5d
  fin_emergency_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = draws %>% filter(i == 21) %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "financially transparent environment - not financially transparent emergency" = 
      (fin_transparency + environment),
    "financially transparent human rights - not financially transparent emergency" = 
      (fin_transparency + human_rights),
    "financially transparent refugee relief - not financially transparent emergency" = 
      (fin_transparency + refugee_relief),
    "criticized financially transparent environment - criticized not financially transparent emergency" = 
      (fin_transparency + environment + criticized + fin_environment_criticized) - (criticized),
    "criticized financially transparent human rights - criticized not financially transparent emergency" = 
      (fin_transparency + human_rights + criticized + fin_humanrights_criticized) - (criticized),
    "criticized financially transparent refugee relief - criticized not financially transparent emergency" = 
      (fin_transparency + refugee_relief + criticized + fin_refugee_criticized) - (criticized),
    "crackdown financially transparent environment - crackdown not financially transparent emergency" = 
      (fin_transparency + environment + crackdown + fin_environment_crackdown) - (crackdown),
    "crackdown financially transparent human rights - crackdown not financially transparent emergency" = 
      (fin_transparency + human_rights + crackdown + fin_humanrights_crackdown) - (crackdown),
    "crackdown financially transparent refugee relief - crackdown not financially transparent emergency" = 
      (fin_transparency + refugee_relief + crackdown + fin_refugee_crackdown) - (crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "financially transparent environment - not financially transparent emergency":"crackdown financially transparent refugee relief - crackdown not financially transparent emergency", 
    names_to = "level", values_to = "Gamma") %>% 
  mutate(level = fct_rev(fct_inorder(level))) %>%
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

There is no increased willingness to donate to NGOs that are criticized or under government crackdown when they are also financially transparent and work in less contentious areas, holding every other attribute constant.

#### Hypothesis 5e, Relationship with Host Government, Financial Transparency, Issue Area, and Funding Sources

@@

```{r contrasts-hypothesis05e}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds"))

# Reference Level = No financial transparency
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response
# Reference Level = Funded primarily by many small private donations
contrasts_int <- tibble(
  # Attribute levels
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
